Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-08-22 referee.tex
Adjusted referee responses.

\usepackage{fullpage}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{listings,color}
\usepackage{mdframed}
\parskip=10pt

@@

1) One of the main points of the paper is studying the multiplicity of Pop III stars in a halo. This multiplicity might be due to the fact that Pop III stars have collapsed to a BH after their lifetime and a second Pop III star could form in the same halo. This is very plausible. If several Pop III stars are found forming in the same halo at the same time, however, the employed star particle algorithm has a hard-coded length scale of 1pc in which only one star particle can be formed. I am wondering if this is an effect that is resolution dependent - do the same number of stars form if the resolution is increased and the maximum distance is decreased? Which is the motivation for the length scale of 1pc?
\end{referee}

@@

\begin{referee}
2) The authors select their haloes by the halo finding algorithm Rockstar. They should add a bit of information on that code (is it fof or subfind-like?). Also, one of their main points is to compare their work to Machacek+01. Machacek+01, however, use a different halo definition (spherical around the halo centre going out to a radius of 200 times the mean density of the Universe). How do these different halo masses compare?

Further, it is not entirely clear why atomic cooling haloes are excluded in this analysis and if they are excluded throughout the whole paper. The exclusion of atomic cooling haloes artificially shifts the average halo mass to lower values.

In addition, the authors should state the fraction of haloes that have Pop III stars forming outside the halo. The baryon fraction varies with redshift. Please give an estimate by how much this influences the halo masses used here.
\end{referee}

@@

\begin{figure}
	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{images/compare_halo_mass.pdf}
    \label{fig:compare_mass}
\end{figure}

@@

The authors should state at one point in the paper for which properties they use comoving or physical units.
\end{referee}
This has been clarified at the end of the second paragraph in the Simulation Setup section.

@@

The authors write that Pop III star formation is generally more massive. While a fraction of the community agrees with that, there is manifoldly cited work that finds low-mass Pop III progenitors, and the authors should not let that unmentioned, but also cite eg Stacy+16, Greif+11 and Clark+11.
\end{referee}
These studies have been mentioned and cited in the introcution.

\begin{referee}
The authors name a few processes for suppressing Pop III star formation. For completeness, they should also mention eg X-ray heating (citing eg Jeon+14).
\end{referee}
This study has been mentioned and cited in the introduction.

\begin{referee}
The authors cite the well-known study from Machacek+01. However, a more recent result would be from the study by Visbal+14, giving a lower mass limit. Since the authors find a lower mass limit than Machacek+01, it would be interesting to see how this compares to the lower mass limit from the more modern paper.
\end{referee}
We have included the $M_{\rm crit}$ function that Visbal+14 use in their study (their Equation 4) for a redshift of 20 as a solid purple line in Figure 10. It appears the Visbal+14 find similar masses as Machacek+01, and when comparing the Machacek+01 for our LWBG and the relation from Visbal+14 at z=20, Visbal+14 find higher halo masses overall.

@@

In Wise+12, three different environment regions are picked. Please provide more description on the rare peak simulation here and discuss why this one is appropriate in this context.
\end{referee}
RP stands for radiation pressure in Wise+12, not rare peak. The simulation is the same size as ours, and contains similar physics, including the radiation pressure and soft UV background, which is why we reference it here. The differences are the inclusion of H2 self-shielding and updated cosmological parameters.

\begin{referee}
The initialization at z=130 is very late. I am aware that it is impossible to repeat this simulation starting at an earlier redshift, but would advise for future work.
\end{referee}

@@

\begin{referee}
Why do the authors pick a non-zero metalicity threshold for Pop III star formation? How many Pop III stars form between Z=0 and Z=5e-6 Z\_sol?
\end{referee}

@@

\begin{referee}
What is the physical motivation for a density threshold of 1.e6/cc? Is there convergence?
\end{referee}

@@

\begin{referee}
Similarly, why do the authors chose a H2 fraction of 1.e-3? (Is is a mass fraction or a number fraction?) How many Pop III stars do not form because of this threshold?
\end{referee}

@@

\begin{referee}
Do the authors set fixed mass limits to the IMF and if yes, which are they?  If not, which is the highest / lowest mass they find in their random sampling?  And which fraction of the Pop III stars in the simulation end up as type II SNe / BHs / PISN?
\end{referee}
We do set fixed mass limits, between 1 and 300 $M_{\odot}$. We have added this detail in section 2.2.1.

@@

\begin{referee}
One effect than can weaken the shielding is shifting out of the Lyman-Werner resonance lines (see Hartwig+15). I am wondering how much this would affect the study presented here.
\end{referee}
-Would like to discuss this more in detail with John.

\begin{referee}
In Figure 1, please mention in the caption or at the top / bottom of the left axis that a shielding factor of 1 corresponds to no shielding and a shielding factor of 0 corresponds to high shielding, as these nomenclatures are not immediately understandable for the reader.
\end{referee}
This is a tricky detail, and has been added to the caption of Figure 1.

\begin{referee}
The analytic calculation of the shielding factor is a nice property of the paper. However, assuming a constant H2 fraction seems not appropriate. Please repeat this exercise for a more realistic halo profile, which could be found in the simulations or in the literature, eg by Machacek+01 themselves.
\end{referee}
This is a good point, and the plot has been adjusted accordingly. The halo profiles from O'Shea and Norman 2007 are now being used as the \hh{} fraction as a function of radius. The plot now shows that the shielding factor increases as a function of mass, since at larger radii, there is less \hh{}, resulting in a less effective \hh{} shield. The overall take away of the plot has not changed.

@@

Figure 2 is quite empty, it would be useful to include the halo mass function of the earliest Pop III formation redshift with its analytic prediction. In addition, the authors could provide a line or an arrow to show their halo mass resolution limit.
\end{referee}
We have added a vertical line at $10^5 M_{\odot}$ to show our halo mass resolution limit. This detail has also been added to the caption.

@@

\begin{referee}
Figure 3 looks very nice. It would be helpful if an additional line that only 
provides the global LWBG (in units of J21) was included.
\end{referee}
Thank you for your comment. The global LWBG has been added as a red dashed line. More detail about the LW background (solid red line) has also been added.

\begin{referee}
The authors find no correlation between the host halo mass and the Lyman-Werner background intensity. However, they only look at the LWBG flux at the time of Pop III formation - is there maybe a correlation between the time integrated LW flux?
\end{referee}
While the time integrated LW flux would be interesting to follow, and may provide some further insight to what we are exploring, this would be difficult to calculate. It would require constant tracking of halos through time to calculate the time integrated LW flux.

\begin{referee}
Figures 7 and 8 show very nice histograms as an additional panel on the right.  I suggest to include a histogram on the spread of the creation time in Figure 9 similar to Figures 7 and 8.
\end{referee}
The side histogram has been added to Figure 9.

@@

The authors give three reasons for the halo mass spread. Can they estimate which of the three processes (BH formation, dynamical heating and temporal LWBG fluctuations) is responsible for the spread by which fraction?
\end{referee}

@@

\begin{referee}
One of the most extensive studies on over 1000 minihaloes was performed by Hirano+15, who also include a Lyman-Werner background. Their work should be put in comparison as well.
\end{referee}
This study has been added and cited in the Comparison section.
-Should more be added?

\begin{referee}
In Figure 10, the result from Yoshida+03 is hard to see, maybe use a different symbol / colour.
\end{referee}
This has been adjusted. The point from Yoshida+03 is now a pentagon and is outlined in black, and all symbols have had their edges increased for visibility.

\begin{referee}
Since the authors study star formation in minihaloes, it would be appropriate to also mention Kitayama+04 and Schauer+15 for the Lyman-Werner escape fractions from minihaloes.
\end{referee}
These papers have been added and referenced in the first paragraph of the caveats section.

\begin{referee}
The authors mention a few times that streaming velocities are another pathway of suppressing Pop III formation (also in the introduction). While they cite some older work, they however fail to compare to more recent work eg by Hirano+18 or Schauer+19 (who do perform a systematic study not only based on a few, single haloes).
\end{referee}
The Schauer+19 study has been added to the caveat section.

>>>>

\usepackage{fullpage}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{listings,color}
\usepackage{mdframed}
\usepackage{float}
\parskip=10pt

@@

A -- 1) One of the main points of the paper is studying the multiplicity of Pop III stars in a halo. This multiplicity might be due to the fact that Pop III stars have collapsed to a BH after their lifetime and a second Pop III star could form in the same halo. This is very plausible. If several Pop III stars are found forming in the same halo at the same time, however, the employed star particle algorithm has a hard-coded length scale of 1pc in which only one star particle can be formed. I am wondering if this is an effect that is resolution dependent - do the same number of stars form if the resolution is increased and the maximum distance is decreased? Which is the motivation for the length scale of 1pc?
\end{referee}

@@

\begin{referee}
B -- 2) The authors select their haloes by the halo finding algorithm Rockstar. They should add a bit of information on that code (is it fof or subfind-like?). Also, one of their main points is to compare their work to Machacek+01. Machacek+01, however, use a different halo definition (spherical around the halo centre going out to a radius of 200 times the mean density of the Universe). How do these different halo masses compare?

C -- Further, it is not entirely clear why atomic cooling haloes are excluded in this analysis and if they are excluded throughout the whole paper. The exclusion of atomic cooling haloes artificially shifts the average halo mass to lower values.

D -- In addition, the authors should state the fraction of haloes that have Pop III stars forming outside the halo. The baryon fraction varies with redshift. Please give an estimate by how much this influences the halo masses used here.
\end{referee}

@@

\begin{figure}[H]
	\centering
	\includegraphics[keepaspectratio=true, scale=0.5]{images/compare_halo_mass.pdf}
    \label{fig:compare_mass}
\end{figure}

@@

E -- The authors should state at one point in the paper for which properties they use comoving or physical units.
\end{referee}
This has been clarified at the end of the second paragraph in the Simulation Setup section.

@@

F -- The authors write that Pop III star formation is generally more massive. While a fraction of the community agrees with that, there is manifoldly cited work that finds low-mass Pop III progenitors, and the authors should not let that unmentioned, but also cite eg Stacy+16, Greif+11 and Clark+11.
\end{referee}
These studies have been mentioned and cited in the introcution.

\begin{referee}
G -- The authors name a few processes for suppressing Pop III star formation. For completeness, they should also mention eg X-ray heating (citing eg Jeon+14).
\end{referee}
This study has been mentioned and cited in the introduction.

\begin{referee}
H -- The authors cite the well-known study from Machacek+01. However, a more recent result would be from the study by Visbal+14, giving a lower mass limit. Since the authors find a lower mass limit than Machacek+01, it would be interesting to see how this compares to the lower mass limit from the more modern paper.
\end{referee}
We have included the $M_{\rm crit}$ function that Visbal+14 use in their study (their Equation 4) for a redshift of 20 as a solid purple line in Figure 10. It appears the Visbal+14 find similar masses as Machacek+01, and when comparing the Machacek+01 for our LWBG and the relation from Visbal+14 at z=20, Visbal+14 find higher halo masses overall.

@@

I -- In Wise+12, three different environment regions are picked. Please provide more description on the rare peak simulation here and discuss why this one is appropriate in this context.
\end{referee}
RP stands for radiation pressure in Wise+12, not rare peak. The simulation is the same size as ours, and contains similar physics, including the radiation pressure and soft UV background, which is why we reference it here. The differences are the inclusion of H2 self-shielding and updated cosmological parameters.

\begin{referee}
J -- The initialization at z=130 is very late. I am aware that it is impossible to repeat this simulation starting at an earlier redshift, but would advise for future work.
\end{referee}

@@

\begin{referee}
K -- Why do the authors pick a non-zero metalicity threshold for Pop III star formation? How many Pop III stars form between Z=0 and Z=5e-6 Z\_sol?
\end{referee}

@@

\begin{referee}
L -- What is the physical motivation for a density threshold of 1.e6/cc? Is there convergence?
\end{referee}

@@

\begin{referee}
M -- Similarly, why do the authors chose a H2 fraction of 1.e-3? (Is is a mass fraction or a number fraction?) How many Pop III stars do not form because of this threshold?
\end{referee}

@@

\begin{referee}
N -- Do the authors set fixed mass limits to the IMF and if yes, which are they?  If not, which is the highest / lowest mass they find in their random sampling?  And which fraction of the Pop III stars in the simulation end up as type II SNe / BHs / PISN?
\end{referee}
We do set fixed mass limits, between 1 and 300 $M_{\odot}$. We have added this detail in section 2.2.1.

@@

\begin{referee}
O -- One effect than can weaken the shielding is shifting out of the Lyman-Werner resonance lines (see Hartwig+15). I am wondering how much this would affect the study presented here.
\end{referee}
-Would like to discuss this more in detail with John.

\begin{referee}
P -- In Figure 1, please mention in the caption or at the top / bottom of the left axis that a shielding factor of 1 corresponds to no shielding and a shielding factor of 0 corresponds to high shielding, as these nomenclatures are not immediately understandable for the reader.
\end{referee}
This is a tricky detail, and has been added to the caption of Figure 1.

\begin{referee}
Q -- The analytic calculation of the shielding factor is a nice property of the paper. However, assuming a constant H2 fraction seems not appropriate. Please repeat this exercise for a more realistic halo profile, which could be found in the simulations or in the literature, eg by Machacek+01 themselves.
\end{referee}
This is a good point, and the plot has been adjusted accordingly. The halo profiles from O'Shea and Norman 2007 are now being used as the \hh{} fraction as a function of radius. The plot now shows that the shielding factor increases as a function of mass, since at larger radii, there is less \hh{}, resulting in a less effective \hh{} shield. The overall take away of the plot has not changed.

@@

R -- Figure 2 is quite empty, it would be useful to include the halo mass function of the earliest Pop III formation redshift with its analytic prediction. In addition, the authors could provide a line or an arrow to show their halo mass resolution limit.
\end{referee}
We have added a vertical line at $10^5 M_{\odot}$ to show our halo mass resolution limit. This detail has also been added to the caption.

@@

\begin{referee}
S -- Figure 3 looks very nice. It would be helpful if an additional line that only 
provides the global LWBG (in units of J21) was included.
\end{referee}
Thank you for your comment. The global LWBG has been added as a red dashed line. More detail about the LW background (solid red line) has also been added.

\begin{referee}
T -- The authors find no correlation between the host halo mass and the Lyman-Werner background intensity. However, they only look at the LWBG flux at the time of Pop III formation - is there maybe a correlation between the time integrated LW flux?
\end{referee}
While the time integrated LW flux would be interesting to follow, and may provide some further insight to what we are exploring, this would be difficult to calculate. It would require constant tracking of halos through time to calculate the time integrated LW flux.

\begin{referee}
U -- Figures 7 and 8 show very nice histograms as an additional panel on the right.  I suggest to include a histogram on the spread of the creation time in Figure 9 similar to Figures 7 and 8.
\end{referee}
The side histogram has been added to Figure 9.

@@

V -- The authors give three reasons for the halo mass spread. Can they estimate which of the three processes (BH formation, dynamical heating and temporal LWBG fluctuations) is responsible for the spread by which fraction?
\end{referee}

@@

\begin{referee}
W -- One of the most extensive studies on over 1000 minihaloes was performed by Hirano+15, who also include a Lyman-Werner background. Their work should be put in comparison as well.
\end{referee}
This study has been added and cited in the Comparison section.
-Should more be added?

\begin{referee}
X -- In Figure 10, the result from Yoshida+03 is hard to see, maybe use a different symbol / colour.
\end{referee}
This has been adjusted. The point from Yoshida+03 is now a pentagon and is outlined in black, and all symbols have had their edges increased for visibility.

\begin{referee}
Y -- Since the authors study star formation in minihaloes, it would be appropriate to also mention Kitayama+04 and Schauer+15 for the Lyman-Werner escape fractions from minihaloes.
\end{referee}
These papers have been added and referenced in the first paragraph of the caveats section.

\begin{referee}
Z -- The authors mention a few times that streaming velocities are another pathway of suppressing Pop III formation (also in the introduction). While they cite some older work, they however fail to compare to more recent work eg by Hirano+18 or Schauer+19 (who do perform a systematic study not only based on a few, single haloes).
\end{referee}
The Schauer+19 study has been added to the caveat section.
